---
title: "iFood CRM Data Analysis"
output:
  html_document:
    df_print: paged
---

## Libraries

```{r warning=FALSE, message = FALSE}
#load libraries
library(ggcorrplot)
library(rcompanion)
library(effectsize)
library(corrplot)
library(ggplot2)
library(robustbase)
library(litteR)
library(ggpubr)
library(ggstatsplot)
library(flextable)
library(dlookr)
```

## Data reading
```{r}
# Reading data
data <- read.csv('ifood_df.csv')
data <- data[,-c(21,22,23,24,26)] # Deleting unnecessary columns
data <- data[,order(names(data))]
```

## Outlier Detection
I perfomed outlier detection with the use of adjusted boxplots for non normally distributed data
```{r}
# Outlier detection with the adjusted boxplots for non parametric data
dataBox = data
p1 <- ggplot(data = dataBox, aes(x="", y=Age, fill = 'darkred')) + stat_adj_boxplot() + stat_adj_boxplot_outlier() + xlab('Age') + ylab('') + theme(legend.position = "none")
p2 <- ggplot(data = dataBox, aes(x="", y=Income, fill = 'darkred')) + stat_adj_boxplot() + xlab('Income') + ylab('') + theme(legend.position = "none")
p3 <- ggplot(data = dataBox, aes(x="", y=Kidhome, fill = 'darkred')) + stat_adj_boxplot() + xlab('Kidhome') + ylab('') + theme(legend.position = "none")
p4 <- ggplot(data = dataBox, aes(x="", y=MntFishProducts, fill = 'darkred')) + stat_adj_boxplot() + xlab('MntFishProducts') + ylab('') + theme(legend.position = "none")
p5 <- ggplot(data = dataBox, aes(x="", y=MntFruits, fill = 'darkred')) + stat_adj_boxplot() + xlab('MntFruits') + ylab('') + theme(legend.position = "none") + theme(legend.position = "none")
p6 <- ggplot(data = dataBox, aes(x="", y=MntGoldProds, fill = 'darkred')) + stat_adj_boxplot() + xlab('MntGoldProds') + ylab('') + stat_adj_boxplot_outlier() + theme(legend.position = "none")
p7 <- ggplot(data = dataBox, aes(x="", y=MntMeatProducts, fill = 'darkred')) + stat_adj_boxplot() + xlab('MntMeatProducts') + ylab('') + theme(legend.position = "none")
p8 <- ggplot(data = dataBox, aes(x="", y=MntRegularProds, fill = 'darkred')) + stat_adj_boxplot() + xlab('MntRegularProds') + ylab('') + stat_adj_boxplot_outlier() + theme(legend.position = "none")
p9 <- ggplot(data = dataBox, aes(x="", y=MntSweetProducts, fill = 'darkred')) + stat_adj_boxplot() + xlab('MntSweetProducts') + ylab('') + theme(legend.position = "none")
p10 <- ggplot(data = dataBox, aes(x="", y=MntTotal, fill = 'darkred')) + stat_adj_boxplot() + xlab('MntTotal') + ylab('') + theme(legend.position = "none")
p11 <- ggplot(data = dataBox, aes(x="", y=MntWines, fill = 'darkred')) + stat_adj_boxplot() + xlab('MntWines') + ylab('') + theme(legend.position = "none")
p12 <- ggplot(data = dataBox, aes(x="", y=NumCatalogPurchases, fill = 'darkred')) + stat_adj_boxplot() + xlab('NumCatalogPurchases') + ylab('') + stat_adj_boxplot_outlier() + theme(legend.position = "none")
p13 <- ggplot(data = dataBox, aes(x="", y=NumDealsPurchases, fill = 'darkred')) + stat_adj_boxplot() + stat_adj_boxplot_outlier() + xlab('NumDealsPurchases') + ylab('') + theme(legend.position = "none")
p14 <- ggplot(data = dataBox, aes(x="", y=NumStorePurchases, fill = 'darkred')) + stat_adj_boxplot() + xlab('NumStorePurchases') + ylab('') + stat_adj_boxplot_outlier() + theme(legend.position = "none")
p15 <- ggplot(data = dataBox, aes(x="", y=NumWebPurchases, fill = 'darkred')) + stat_adj_boxplot() + xlab('NumWebPurchases') + ylab('') + stat_adj_boxplot_outlier() + theme(legend.position = "none")
p16 <- ggplot(data = dataBox, aes(x="", y=NumWebVisitsMonth, fill = 'darkred')) + stat_adj_boxplot() + stat_adj_boxplot_outlier() + xlab('NumWebVisitsMonth') + ylab('') + stat_adj_boxplot_outlier() + theme(legend.position = "none")


theme_set(theme_pubr())
ggarrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, p13, p14, p15, p16)


# Removing outliers
outliers <- c(44, 1151, 677, 728, 976, 1825, 2181, 401, 895, 1144, 376, 902, 909, 1331, 2062, 1873, 1950)
deals = which(data$NumDealsPurchases >= 7)
store = which(data$NumStorePurchases <= 1)
webVisit = which(data$NumWebVisitsMonth >= 10)

outs <- c(outliers, deals, store, webVisit)
outs <- unique(outs)
dataOut <- data[-c(outs),]
```
## QQ_Plots
We can see here some rigth and over skewness
```{r}
# QQ-Plots for choosed features
qqnorm(dataOut$Income, pch = 1, frame = FALSE, main = 'Income')
qqline(dataOut$Income, col = "steelblue", lwd = 2)

qqnorm(dataOut$Age, pch = 1, frame = FALSE, main = 'Age')
qqline(dataOut$Age, col = "steelblue", lwd = 2)

qqnorm(dataOut$MntMeatProducts, pch = 1, frame = FALSE, main = 'MntMeatProducts')
qqline(dataOut$MntMeatProducts, col = "steelblue", lwd = 2)

qqnorm(dataOut$MntSweetProducts, pch = 1, frame = FALSE, main = 'MntSweetProducts')
qqline(dataOut$MntSweetProducts, col = "steelblue", lwd = 2)

```
## Biserial correlation
I calculated biserial correlation between each campaing and other feathers to find what made costumers to participate in promotion
```{r}
# Calculating biserial correlation
dataOutCor <- dataOut[,c(1:15, 25:34)]
cols <- colnames(dataOutCor)
correlations <- data.frame(AcceptedCmp1 = seq(0,0, length = 25), AcceptedCmp2 = seq(0,0, length = 25),
                           AcceptedCmp3 = seq(0,0, length = 25), AcceptedCmp4 = seq(0,0, length = 25),
                           AcceptedCmp5 = seq(0,0, length = 25), feature = colnames(dataOutCor))
rownames(correlations) <- correlations$feature

for (i in cols){
  #print(data[,i])
  cor <- wilcoxonRG(dataOut[,i], as.factor(dataOut$AcceptedCmp1))
  correlations[i,1] = as.numeric(cor)
}

for (i in cols){
  #print(data[,i])
  cor <- wilcoxonRG(dataOut[,i], as.factor(dataOut$AcceptedCmp2))
  correlations[i,2] = as.numeric(cor)
}

for (i in cols){
  #print(data[,i])
  cor <- wilcoxonRG(dataOut[,i], as.factor(dataOut$AcceptedCmp3))
  correlations[i,3] = as.numeric(cor)
}

for (i in cols){
  #print(data[,i])
  cor <- wilcoxonRG(dataOut[,i], as.factor(dataOut$AcceptedCmp4))
  correlations[i,4] = as.numeric(cor)
}

for (i in cols){
  #print(data[,i])
  cor <- wilcoxonRG(dataOut[,i], as.factor(dataOut$AcceptedCmp5))
  correlations[i,5] = as.numeric(cor)
}
correlationsMatrix <- as.matrix(correlations[,-c(6)])
correlationsMatrix <- t(correlationsMatrix)
correlationsMatrix <- correlationsMatrix *(-1)

corrplot(correlationsMatrix, method="color", addCoef.col = "black")
```

## Kruskal-Wallis tests
Anova-like test(for non-parametric data) to find any differences between groups 
```{r}
# Kruskal-Wallis tests
ggbetweenstats(data = dataOut,
               x=  AcceptedCmpOverall,
               y= Income,
               type = "nonparametric",
               pairwise.display = "significant",
               p.adjust.method = "holm")

ggbetweenstats(data = dataOut,
               x=  AcceptedCmpOverall,
               y= Age,
               type = "nonparametric",
               pairwise.display = "significant",
               p.adjust.method = "holm")

ggbetweenstats(data = dataOut,
               x=  AcceptedCmpOverall,
               y= Recency,
               type = "nonparametric",
               pairwise.display = "significant",
               p.adjust.method = "holm")
```



